---
title: "Tagged variables in TOPMed"
author: "Leslie Emery"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document:
        toc: true
        toc_depth: 5
        toc_float: true
        number_sections: true
        code_folding: hide
        theme: cerulean
        keep_md: true
---
<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>


```{r setup, message=FALSE}
knitr::opts_chunk$set(tidy=FALSE)
library(tidyverse)
library(RColorBrewer)

data_file <- 'tagged_variables.txt'
```

# Overview of the data
Input data file: ``r data_file``

The input data was exported from the PIE production database using a `python` script. Some minimal pre-processing of the data (mostly removing non-ASCII characters from the user-input comment fields) was performed in that `python` script.

I read in the data using the `tidyverse` `readr` function. After examining the data, I set the data type for each column, including setting up many of the categorical variables to be factors with automatically detected factor levels.

```{r read-data, results='hide'}
tagged_variable_col_types <- cols(
  tag_id = col_factor(NULL),
  tag_title = col_factor(NULL),
  variable_phv = col_character(),
  variable_name = col_character(),
  variable_description = col_character(),
  dataset_pht = col_character(),
  dataset_name = col_character(),
  dataset_description = col_character(),
  study_name = col_factor(NULL),
  study_phs = col_factor(NULL),
  tagged_by = col_character(),
  created = col_datetime(format = ""),
  modified = col_datetime(format = ""),
  dcc_review_status = col_factor(NULL),
  dcc_review_comment = col_character(),
  dcc_review_creator = col_factor(NULL),
  study_response_status = col_factor(NULL),
  study_response_comment = col_character(),
  study_response_creator = col_character(),
  is_archived = col_logical(),
  milestone = col_factor(NULL)
)
all_tagged_variables <- read_tsv(data_file, na=c('', 'None'), col_types=tagged_variable_col_types)
problems(all_tagged_variables)  # No problems!
```

Then I customized the factor levels for the `milestone`, `dcc_review_status`, and `study_response_status` columns. I confirmed the factor levels had been changed accurately by comparing bar plots of each variable before and after the level changes.
```{r set-factor-levels, results='hold'}
# Order the milestone levels properly.
ggplot(all_tagged_variables) + geom_bar(aes(x=milestone))
all_tagged_variables <- all_tagged_variables %>% 
    mutate(milestone=fct_relevel(milestone, c('1', '2', '3', '4')))
ggplot(all_tagged_variables) + geom_bar(aes(x=milestone))

# Add sensible labels for the DCC status levels.
ggplot(all_tagged_variables) + geom_bar(aes(x=dcc_review_status))
all_tagged_variables <- all_tagged_variables %>%
    mutate(dcc_review_status=recode_factor(dcc_review_status, !!!list('1'='confirmed', '0'='needs study followup')))
ggplot(all_tagged_variables) + geom_bar(aes(x=dcc_review_status))

# Add sensible labels for the study response status levels.
ggplot(all_tagged_variables) + geom_bar(aes(x=study_response_status))
all_tagged_variables <- all_tagged_variables %>%
    mutate(study_response_status=recode_factor(study_response_status, !!!list('1'='agreed to remove', '0'='gave explanation')))
ggplot(all_tagged_variables) + geom_bar(aes(x=study_response_status))
```

While I've previously included only the studies that were funded for tagging through subcontracts, for my current analysis I'd like to take a look at all of the studies.

I added some study abbreviations for concise display.
```{r set-study-abbreviations}
study_shortnames <- c('MESA' = 209, 'JHS' = 286, 'ARIC' = 280, 'CHS' = 287, 'WHI' = 200, 'FHS' = 7, 'CARDIA' = 285,
                      'COPDGene' = 179, 'CFS' = 284, 'Mayo_VTE' = 289, 'GOLDN' = 741, 'HCHS/SOL' = 810,
                      'SAS' = 914, 'Amish' = 956, 'CRA' = 988, 'HVH' = 1013, 'GENOA' = 1238)
study_shortnames <- study_shortnames[order(names(study_shortnames))]
funded_studies <- c('MESA' = 209, 'JHS' = 286, 'ARIC' = 280, 'CHS' = 287, 'WHI' = 200, 'FHS' = 7, 'CARDIA' = 285)

# Add a study_shortname column.
phs_to_shortname <- names(study_shortnames)
names(phs_to_shortname) <- as.character(study_shortnames)
phs_to_shortname <- as.list(phs_to_shortname)
tagged_variables <- all_tagged_variables %>% 
    mutate(study_shortname=recode_factor(study_phs, !!!phs_to_shortname))
```

## Final cleaned dataset
```{r print-cleaned-data, results='hold'}
options(width=400)
print(tagged_variables, n_extra=30)
```

# Exploratory visualization
```{r visual-settings}
# Save variables to use for determining plot size.
panel_width <- 7
panel_asp <- (9/16)
# Set the default plot size.
knitr::opts_chunk$set(fig.width=panel_width, fig.asp=panel_asp, dpi=300)
# Save some ggplot layers for convenience (will reuse many times).
current_theme <- theme_bw()
angled_x_axis_labels <- theme(axis.text.x=element_text(angle=60, hjust=1))
legend_on_top <- theme(legend.position='top')
no_legend <- theme(legend.position='none')
# Save some color palettes and manual fill scales for reuse.
study_colors <- c(brewer.pal(8, 'Set2'), brewer.pal(9, 'Set1'))[1:length(levels(tagged_variables$study_shortname))]
names(study_colors) <- levels(tagged_variables$study_shortname)
study_fill <- scale_fill_manual(values=study_colors)
milestone_colors <- brewer.pal(length(levels(tagged_variables$milestone)), 'Dark2')
names(milestone_colors) <- levels(tagged_variables$milestone)
milestone_fill <- scale_fill_manual(values=milestone_colors)
bar_border_color <- 'gray25'
# Save ggplot layer for facet wrapping by milestone, with prettier labels.
longer_milestone_labels <- paste('Milestone', levels(tagged_variables$milestone))
names(longer_milestone_labels) <- levels(tagged_variables$milestone)
milestone_facets <- facet_wrap(~ milestone, scales='free', ncol=1, labeller=labeller(milestone=longer_milestone_labels))
```

## Total number of variables tagged
```{r number-of-variables}
n_unique_variables <- length(unique(tagged_variables$variable_phv))
n_tagged_variables <- nrow(tagged_variables)
```
There are `r n_unique_variables` unique dbGaP variables that have been tagged.
There is a total of `r n_tagged_variables` tag-variable pairings.

## Number of variables tagged by study
```{r tagged-var-count-by-study}
tagged_variable_counts_by_study <- 
    tagged_variables %>% 
    group_by(study_shortname, study_name) %>% 
    summarize(tagged_variable_count=n())

# # Reorder study by decreasing tagged variable count.
# tagged_variables$study_shortname <- factor(tagged_variables$study_shortname, levels=tagged_variable_counts_by_study$study_shortname[order(-tagged_variable_counts_by_study$tagged_variable_count)])

tagged_variable_counts_by_study_ggp <- 
    ggplot(tagged_variables) +
    geom_bar(aes(x=study_shortname, fill=study_shortname), color=bar_border_color) +
    study_fill +
    current_theme +
    angled_x_axis_labels +
    no_legend
```    

```{r tagged-var-count-by-study-table, results='asis'}
knitr::kable(tagged_variable_counts_by_study, align='c')
```

```{r tagged-var-count-by-study-plot}
print(tagged_variable_counts_by_study_ggp)
```

## Total number of variables per study
```{r total-vars}
totals_fn <- 'total_traits.txt'
total_variables <- read_tsv(totals_fn)

total_variables_and_tagged_counts <- inner_join(total_variables, tagged_variable_counts_by_study)

total_variables_and_tagged_counts_ggp <- 
    ggplot(total_variables_and_tagged_counts) +
    geom_col(aes(x=study_shortname, y=tagged_variable_count/n_variables, fill=study_shortname), color=bar_border_color) +
    study_fill +
    current_theme +
    angled_x_axis_labels +
    ylab('Proportion of variables tagged') +
    xlab('Study') +
    no_legend

# proportional to number of variables
    # ggplot(total_variables_and_tagged_counts, aes(x=study_shortname, y=tagged_variable_count/n_variables, width=log(n_variables)/10)) +
    # geom_bar(aes(fill=study_shortname), color=bar_border_color, stat='identity', position='identity') +
    # study_fill +
    # current_theme +
    # angled_x_axis_labels +
    # no_legend
```

```{r proportion-tagged-plot}
print(total_variables_and_tagged_counts_ggp)
```

## Number of variables tagged by tag
This is split by milestone just to make it easier to see all of the tags at once.
```{r tagged-var-count-by-tag}
tagged_variable_counts_by_tag <- 
    tagged_variables %>% 
    group_by(tag_title, milestone) %>% 
    summarize(tagged_variable_count=n())

# Reorder tag by decreasing tagged variable count.
tagged_variables$tag_title <- factor(tagged_variables$tag_title, levels=tagged_variable_counts_by_tag$tag_title[order(-tagged_variable_counts_by_tag$tagged_variable_count)])

tagged_variable_counts_by_tag_ggp <- 
    ggplot(tagged_variables) +
    geom_bar(aes(x=tag_title, fill=milestone), color=bar_border_color) +
    milestone_fill +
    milestone_facets +
    current_theme +
    angled_x_axis_labels +
    no_legend

tagged_variable_counts_by_tag_ggp_horiz <- 
    ggplot(tagged_variables) +
    geom_bar(aes(x=tag_title, fill=milestone), color=bar_border_color) +
    milestone_fill +
    facet_wrap(~ milestone, scales='free', ncol=2, labeller=labeller(milestone=longer_milestone_labels)) +
    current_theme +
    angled_x_axis_labels +
    no_legend
```

```{r tagged-var-count-by-tag-table, results='asis'}
knitr::kable(tagged_variable_counts_by_tag, align='c')
```

```{r tagged-var-count-by-tag-plot, fig.width=panel_width, fig.height=panel_width*panel_asp*length(levels(tagged_variables$milestone)), fig.asp=NULL}
print(tagged_variable_counts_by_tag_ggp)
```

```{r tagged-var-count-by-tag-plot-horiz, fig.width=panel_width*2, fig.height=panel_width*panel_asp*2, fig.asp=NULL}
print(tagged_variable_counts_by_tag_ggp_horiz)
```

## Number of variables tagged in each milestone
```{r tagged-var-count-by-milestone}
tagged_variable_counts_by_milestone <-
    tagged_variables %>% 
    group_by(milestone) %>% 
    summarize(tagged_variable_count=n())

# # Reorder milestone by decreasing tagged variable count.
# tagged_variables$milestone <- factor(tagged_variables$milestone, levels=tagged_variable_counts_by_milestone$milestone[order(-tagged_variable_counts_by_milestone$tagged_variable_count)])
# This looked nice, but was close enough to the number ordering to be confusing.

tagged_variable_counts_by_milestone_ggp <-
    ggplot(tagged_variables) +
    geom_bar(aes(x=milestone, fill=milestone), color=bar_border_color) +
    milestone_fill +
    current_theme +
    no_legend
```

```{r tagged-var-count-by-milestone-table, results='asis'}
knitr::kable(tagged_variable_counts_by_milestone, align='c')
```

```{r tagged-var-count-by-milestone-plot}
print(tagged_variable_counts_by_milestone_ggp)
```

## Examine the number of tagged variables per study in detail for each tag
```{r tagged-var-count-by-study-and-tag}
tagged_variable_counts_by_study_and_tag <-
    tagged_variables %>%
    group_by(study_shortname, tag_title, milestone) %>% 
    summarize(tagged_variable_count=n())

# Reorder tags by decreasing tagged variable count.
tagged_variable_counts_by_study_and_tag$tag_title <- factor(tagged_variable_counts_by_study_and_tag$tag_title, levels=tagged_variable_counts_by_tag$tag_title[order(-tagged_variable_counts_by_tag$tagged_variable_count)])
# Make study a factor, for discrete scale.
tagged_variable_counts_by_study_and_tag$study_shortname <- factor(tagged_variable_counts_by_study_and_tag$study_shortname)

tag_columns <- 5
tagged_variable_counts_by_study_and_tag_ggp <-
    ggplot(tagged_variable_counts_by_study_and_tag) +
    geom_bar(aes(x=study_shortname, y=tagged_variable_count, fill=study_shortname), stat='identity', color=bar_border_color) +
    study_fill +
    facet_wrap(~ tag_title, scales='free_y', ncol=tag_columns) +
    current_theme +
    legend_on_top +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          strip.text=element_text(size=rel(0.75))
    )
#     theme(axis.text.y=element_text(size=rel(3.5)),
#           axis.title=element_text(size=rel(5)),
#           axis.text.x=element_blank(),
#           axis.title.x=element_blank(),
#           legend.title=element_text(size=rel(5)),
#           legend.text=element_text(size=rel(5)),
#           strip.text=element_text(size=rel(2.75)),
#           legend.key.height=unit(5, 'points'),
#           legend.key.width=unit(30, 'points')
#     )
```

```{r tagged-var-count-by-study-and-tag-table, results='asis'}
knitr::kable(tagged_variable_counts_by_study_and_tag[order(-tagged_variable_counts_by_study_and_tag$tagged_variable_count), ], align='c')
```

```{r tagged-var-count-by-study-and-tag-plot, fig.width=tag_columns*panel_width*0.25, fig.height=panel_asp*panel_width*(length(levels(tagged_variables$tag_title))/tag_columns)*0.25, fig.asp=NULL}
print(tagged_variable_counts_by_study_and_tag_ggp)
```

```{r tagged-var-count-for-specific-tags}
tags_to_plot <- c('Medication/supplement use')
# tag <- tags_to_plot[1]
for (tag in tags_to_plot)
{
    specific_tag_tagged_variable_count_by_study_ggp <-
        ggplot(tagged_variable_counts_by_study_and_tag %>% subset(tag_title == tag) ) +
        geom_bar(aes(x=study_shortname, y=tagged_variable_count, fill=study_shortname), stat='identity', color=bar_border_color) +
        study_fill +
        current_theme +
        no_legend +
        ggtitle(tag)
    print(specific_tag_tagged_variable_count_by_study_ggp)
}
```

## Number of variables tagged for each tag, by milestone and study
```{r tagged-variable-counts-by-study-and-tag-and-milestone}
# Reorder tags by milestone and decreasing tagged variable count.
tagged_variable_counts_by_study_and_tag$tag_title <- factor(tagged_variable_counts_by_study_and_tag$tag_title, levels=tagged_variable_counts_by_tag$tag_title[order(tagged_variable_counts_by_tag$milestone, -tagged_variable_counts_by_tag$tagged_variable_count)])

tagged_variable_counts_by_study_and_tag_fill_by_milestone_ggp <-
    ggplot(tagged_variable_counts_by_study_and_tag) +
    geom_bar(aes(x=tag_title, y=tagged_variable_count, fill=milestone), stat='identity', color=bar_border_color) +
    facet_grid(study_shortname ~ ., scales='free_y') +
    current_theme +
    angled_x_axis_labels +
    legend_on_top
```

```{r tagged-variable-counts-by-study-and-tag-and-milestone-plot, fig.asp=NULL, fig.width=panel_width*1.5, fig.height=panel_width*panel_asp*length(levels(tagged_variables$study_name))*0.5}
print(tagged_variable_counts_by_study_and_tag_fill_by_milestone_ggp)
```

## Number of variables tagged in each milestone, by study
```{r tagged-var-count-by-milestone-and-study}
tagged_variable_counts_by_milestone_and_study <- 
    tagged_variables %>%
    group_by(study_shortname, milestone) %>% 
    summarize(tagged_variable_count=n())

tagged_variable_counts_by_milestone_and_study_ggp <-
    ggplot(tagged_variable_counts_by_milestone_and_study) +
    geom_bar(aes(x=study_shortname, y=tagged_variable_count, fill=milestone), stat='identity', position='stack', color=bar_border_color) +
    milestone_fill +
    current_theme +
    angled_x_axis_labels +
    legend_on_top
```

```{r tagged-var-count-by-milestone-and-study-table, results='asis'}
knitr::kable(tagged_variable_counts_by_milestone_and_study, align='c')
```

```{r tagged-var-count-by-milestone-and-study-plot}
print(tagged_variable_counts_by_milestone_and_study_ggp)
```

# Progress and usefulness of quality review

The 3-step quality review process only applied to studies that received subcontract funding for completing the tagging. So subset to only the funded studies.

```{r subset-studies}
tagged_variables <- tagged_variables %>%
   subset(study_phs %in% funded_studies) %>% 
   droplevels()
```

## Progress of DCC quality review (step 1)
```{r reviewed-by-milestone}
proportion_reviewed_by_milestone <-
    tagged_variables %>%
    group_by(milestone) %>%
    summarize(tagged_variable_count=n(),
              reviewed_count=sum(!is.na(dcc_review_status)),
              reviewed_proportion=sum(!is.na(dcc_review_status))/n()
    )

proportion_reviewed_by_milestone_ggp <-
    ggplot(proportion_reviewed_by_milestone) +
    geom_bar(aes(x=milestone, y=reviewed_proportion, fill=milestone), stat='identity', color=bar_border_color) +
    milestone_fill +
    current_theme +
    no_legend
```

```{r reviewed-by-milestone-table, results='asis'}
knitr::kable(proportion_reviewed_by_milestone, align='c')
```

```{r reviewed-by-study}
proportion_reviewed_by_study <- 
    tagged_variables %>%
    group_by(study_shortname) %>%
    summarize(tagged_variable_count=n(),
              reviewed_count=sum(!is.na(dcc_review_status)),
              reviewed_proportion=sum(!is.na(dcc_review_status))/n()
    )

proportion_reviewed_by_study_ggp <-
    ggplot(proportion_reviewed_by_study) +
    geom_bar(aes(x=study_shortname, y=reviewed_proportion, fill=study_shortname), stat='identity', color=bar_border_color) +
    study_fill +
    current_theme +
    no_legend
```

```{r reviewed-by-study-table, align='c'}
knitr::kable(proportion_reviewed_by_study, align='c')
```

```{r reviewed-progress-plots}
print(proportion_reviewed_by_milestone_ggp)
print(proportion_reviewed_by_study_ggp)
```

```{r reviewed-by-tag}
completed_review_by_tag <- 
    tagged_variables %>%
    group_by(tag_title, milestone) %>%
    summarize(tagged_variable_count=n(),
              reviewed_count=sum(!is.na(dcc_review_status)),
              reviewed_proportion=sum(!is.na(dcc_review_status))/n()
    )

proportion_reviewed_by_tag_ggp <-
    ggplot(completed_review_by_tag) +
    geom_bar(aes(x=tag_title, y=reviewed_proportion, fill=milestone), color=bar_border_color, stat='identity') +
    milestone_facets +
    current_theme +
    angled_x_axis_labels +
    legend_on_top
```

```{r reviewed-by-tag-table, results='asis'}
knitr::kable(completed_review_by_tag, align='c')
```

```{r reviewed-by-tag-plot, fig.width=panel_width, fig.height=panel_width*panel_asp*length(levels(tagged_variables$milestone)), fig.asp=NULL}
print(proportion_reviewed_by_tag_ggp)
```

```{r reviewed-vs-not-plot}
reviewed_vs_not_ggp <- 
    ggplot(tagged_variables) +
    geom_bar(aes(x=study_shortname, fill=!is.na(dcc_review_status)), color=bar_border_color) +
    scale_fill_brewer(palette='Paired', breaks=c(FALSE, TRUE), labels=c('unreviewed', 'reviewed'), name='DCC review') +
    current_theme +
    legend_on_top
print(reviewed_vs_not_ggp)
```

## What proportion of tagged variables in each study is confirmed by the DCC?
```{r confirmed-proportion-by-study}
review_status_by_study <-
    tagged_variables %>% 
    subset(!is.na(dcc_review_status)) %>% 
    group_by(study_shortname, dcc_review_status) %>% 
    summarize(tagged_variable_count=n())

review_status_by_study_ggp <-
    ggplot(review_status_by_study) +
    geom_bar(aes(x=study_shortname, y=tagged_variable_count, fill=dcc_review_status), stat='identity', position='stack', color=bar_border_color) +
    scale_fill_brewer(palette='Paired', name='DCC review status') +
    current_theme +
    legend_on_top
```

```{r confirmed-proportion-by-study-table, results='asis'}
knitr::kable(review_status_by_study, align='c')
```

```{r confirmed-proportion-by-study-plot}
print(review_status_by_study_ggp)
```

## Is the rate of confirming tagged variables similar across reviewers?
```{r confirmed-proportion-by-reviewer}
review_status_by_reviewer <-
    tagged_variables %>% 
    subset(!is.na(dcc_review_status)) %>% 
    subset(dcc_review_creator != 'Leslie Emery') %>% 
    group_by(dcc_review_creator, dcc_review_status) %>% 
    summarize(tagged_variable_count=n())

review_status_by_reviewer_ggp <-
    ggplot(review_status_by_reviewer) +
    geom_bar(aes(x=dcc_review_creator, y=tagged_variable_count, fill=dcc_review_status), stat='identity', position='stack', color=bar_border_color) +
    scale_fill_brewer(palette='Paired', name='DCC review status') +
    current_theme +
    legend_on_top
```
After looking into this, Jai was working on some of the more straightforward tags (e.g. phenotypes from the common covariates dataset), so they were not flagged for removal as often.

```{r confirmed-proportion-by-reviewer-table, results='asis'}
knitr::kable(review_status_by_reviewer, align='c')
```

```{r confirmed-proportion-by-reviewer-plot}
print(review_status_by_reviewer_ggp)
```

## How does the rate of confirming tagged variables vary between tags?
```{r confirmed-proportion-by-tag}
review_status_by_tag <-
    tagged_variables %>% 
    subset(!is.na(dcc_review_status)) %>% 
    group_by(tag_title, dcc_review_status, milestone) %>% 
    summarize(tagged_variable_count=n())

review_status_by_tag_ggp <-
    ggplot(review_status_by_tag) +
    geom_bar(aes(x=tag_title, y=tagged_variable_count, fill=dcc_review_status), stat='identity', position='stack', color=bar_border_color) +
    scale_fill_brewer(palette='Paired', name='DCC review status') +
    milestone_facets +
    current_theme +
    legend_on_top +
    angled_x_axis_labels

review_status_by_tag_ggp_horiz <-
    ggplot(review_status_by_tag) +
    geom_bar(aes(x=tag_title, y=tagged_variable_count, fill=dcc_review_status), stat='identity', position='stack', color=bar_border_color) +
    scale_fill_brewer(palette='Paired', name='DCC review status') +
    facet_wrap(~ milestone, scales='free', ncol=2, labeller=labeller(milestone=longer_milestone_labels)) +
    current_theme +
    legend_on_top +
    angled_x_axis_labels
```

```{r confirmed-proportion-by-tag-table, results='asis'}
knitr::kable(review_status_by_tag, align='c')
```

```{r confirmed-proportion-by-tag-plot, fig.width=panel_width, fig.height=panel_width*panel_asp*length(levels(tagged_variables$milestone)), fig.asp=NULL}
print(review_status_by_tag_ggp)
```

```{r confirmed-proportion-by-tag-plot-horiz, fig.width=panel_width*2, fig.height=panel_width*panel_asp*2, fig.asp=NULL}
print(review_status_by_tag_ggp_horiz)
```

## Progress of study responses (step 2)
```{r study-response-status-by-study}
study_response_status_by_study <-
    tagged_variables %>%
    subset(dcc_review_status=='needs study followup') %>% 
    group_by(study_shortname, study_phs, study_response_status) %>% 
    summarize(tagged_variable_count=n())

study_response_status_by_study_ggp <- 
    ggplot(tagged_variables %>% subset(dcc_review_status=='needs study followup')) +
    geom_bar(aes(x=study_shortname, fill=study_response_status)) +
    current_theme + 
    angled_x_axis_labels
```

```{r study-response-status-by-study-table, results='asis'}
knitr::kable(study_response_status_by_study, align='c')
```

```{r study-response-status-by-study-plot}
print(study_response_status_by_study_ggp)
```

## Are studies generally agreeing to remove the tagged variables that have been flagged for removal?
```{r study-response-agree-proportion}
study_response_agree_proportion_by_study <-
    tagged_variables %>%
    subset(!is.na(study_response_status)) %>% 
    group_by(study_shortname, study_phs) %>% 
    summarize(response_count=n(),
              agreed_count=sum(study_response_status=='agreed to remove'),
              agreed_proportion=sum(study_response_status=='agreed to remove')/n())

study_response_by_study_without_na_ggp <-
    ggplot(tagged_variables %>% subset(!is.na(study_response_status))) +
    geom_bar(aes(x=study_shortname, fill=study_response_status)) +
    current_theme +
    angled_x_axis_labels
```

```{r study-response-agree-proportion-table, results='asis'}
knitr::kable(study_response_agree_proportion_by_study, align='c')
```

```{r study-response-agree-proportion-plot}
print(study_response_by_study_without_na_ggp)
```

## How does the rate of studies agreeing to removal of tagged variables vary between tags?
```{r study-response-agree-proportion-by-tag}
study_response_agree_proportion_by_tag <-
    tagged_variables %>%
    subset(!is.na(study_response_status)) %>% 
    group_by(tag_id, tag_title, milestone) %>% 
    summarize(response_count=n(),
              agreed_count=sum(study_response_status=='agreed to remove'),
              agreed_proportion=sum(study_response_status=='agreed to remove')/n())

study_response_by_tag_without_na_ggp <-
    ggplot(study_response_agree_proportion_by_tag) +
    geom_bar(aes(x=tag_title, y=agreed_proportion, fill=milestone), stat='identity', position='stack', color=bar_border_color) +
    milestone_facets +
    milestone_fill + 
    current_theme +
    legend_on_top +
    angled_x_axis_labels

```

```{r study-response-agree-proportion-by-tag-table, results='asis'}
knitr::kable(study_response_agree_proportion_by_tag, align='c')
```

```{r study-response-agree-proportion-by-tag-plot, fig.width=panel_width, fig.height=panel_width*panel_asp*length(levels(tagged_variables$milestone)), fig.asp=NULL}
print(study_response_by_tag_without_na_ggp)
```

There's not enough data on this yet.

## Confirmed rate at the end of all reviewing
```{r final-confirmed-proportion-by-tag}
review_status_by_tag <-
    tagged_variables %>% 
    group_by(tag_title, is_archived, milestone) %>% 
    summarize(tagged_variable_count=n())

review_status_by_tag_ggp <-
    ggplot(review_status_by_tag) +
    geom_bar(aes(x=tag_title, y=tagged_variable_count, fill=is_archived), stat='identity', position='stack', color=bar_border_color) +
    scale_fill_brewer(palette='Paired', name='Passed review') +
    milestone_facets +
    current_theme +
    legend_on_top +
    angled_x_axis_labels

highest_non_med_count <- tagged_variables %>%
    group_by(tag_title) %>%
    filter(tag_title != "Medication/supplement use") %>% 
    summarize(count=n()) %>%
    filter(count == max(count))
highest_non_med_count <- highest_non_med_count$count[1]
    
review_status_by_tag_ggp_horiz <-
    ggplot(review_status_by_tag) +
    geom_bar(aes(x=tag_title, y=tagged_variable_count, fill=is_archived), stat='identity', position='stack', color=bar_border_color) +
    scale_fill_brewer(palette='Paired', name='Passed review') +
    facet_wrap(~ milestone, scales='free', ncol=2, labeller=labeller(milestone=longer_milestone_labels)) +
    current_theme +
    legend_on_top +
    angled_x_axis_labels +
    coord_cartesian(ylim=c(0, highest_non_med_count*1.05))
    # ylim(0, highest_non_med_count * 1.05)

# Reorder by tag name instead
# tagged_variables$study_shortname <- factor(tagged_variables$study_shortname, levels=tagged_variable_counts_by_study$study_shortname[order(-tagged_variable_counts_by_study$tagged_variable_count)])
review_status_by_tag$tag_title <- factor(review_status_by_tag$tag_title, levels=sort(levels(review_status_by_tag$tag_title)))
review_status_by_tag <- review_status_by_tag[order(review_status_by_tag$tag_title), ]
review_status_by_tag$in_first_half <- as.numeric(rownames(review_status_by_tag)) >= nrow(review_status_by_tag)/2

review_status_by_tag_ggp_horiz <-
    ggplot(review_status_by_tag) +
    geom_bar(aes(x=tag_title, y=tagged_variable_count, fill=!is_archived), stat='identity', position='stack', color=bar_border_color) +
    scale_fill_brewer(palette='Paired', name='Passed review') +
    facet_wrap(~ in_first_half, scales='free', nrow=2) +
    current_theme +
    legend_on_top +
    angled_x_axis_labels +
    coord_cartesian(ylim=c(0, highest_non_med_count*1.05)) +
    theme(strip.text=element_blank()) +
    ylab('Number of tagged variables') +
    xlab('Tag')
```

```{r review_status_by_tag_ggp_horiz-plot, fig.width=panel_width*2, fig.height=panel_width*(9/16)*length(2)*2, fig.asp=NULL}
print(review_status_by_tag_ggp_horiz)
```


```{r final-confirmed-proportion-by-tag-table, results='asis'}
knitr::kable(review_status_by_tag, align='c')
```
